%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Senior Front-End Engineer}
  {Sigma Software Group}
  {Kyiv, Ukraine}
  {Mar. 2022 -- Present}
  {
    \begin{cvitems}
      \item {\textbf{Healthcare / e-Stock Back Office:} Lead frontend development for an enterprise back-office module, covering technical planning, estimation, implementation, code reviews, delivery coordination, and mentoring backend developers in frontend development.}
      \item {Develop admin functionality for managing access rights, organizations, users, dictionaries, and external system configurations.}
      \item {\textbf{Automotive / GET VD:} Contributed to a data mapping and validation tool, implementing frontend features, maintaining unit tests, and ensuring smooth integration with backend services.}
      \item {Conducted in-depth code reviews, promoted best practices, suggested legacy code refactoring, participated in Agile ceremonies, and conducted technical interviews with structured candidate feedback.}
      \item {\textbf{AI Chatbot / Sima:} Developed admin console functionality for managing chatbot-related data, request history, intents, analytics, statistics, and configuration settings.}
      \item {Implemented interactive data visualizations and user-friendly interfaces to support analytics and operational workflows.}
      \item {\textbf{Automotive / TAPTA:} Implemented image-based vehicle part identification with coordinate-based markers, overlays, and associated OE/GA code display.}
      \item {Improved frontend maintainability by creating reusable UI components and optimizing generic classes for better scalability.}
      \item {\textbf{Insurance / Mobilitu/RedClick:} Developed multi-language and region-aware interfaces for an international vehicle insurance platform, supporting localization and market-specific requirements.}
      \item {Implemented accessibility improvements, maintained CSP rules, frontend unit tests, Storybook documentation, and dev wikis to support quality, security, and onboarding.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Junior Front-End Developer}
  {USENSE}
  {Kyiv, Ukraine}
  {Jul. 2021 -- Mar. 2022}
  {
    \begin{cvitems}
      \item {\textbf{Finance / BlueBilling:} Developed and maintained configurable customer portals for billing account management, invoices, resource consumption, and payments.}
      \item {Implemented reusable frontend libraries shared across multiple portals and supported both standalone and iframe-based portal integrations.}
      \item {Built responsive and configurable user interfaces using Angular and TypeScript, adapting portal behavior and appearance to customer-specific settings.}
      \item {Integrated payment functionality through third-party services and communicated directly with the customer to clarify requirements and support delivery.}
    \end{cvitems}
  }

\end{cventries}